Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum

### 2018-04-19 statistical-quorum.tex
Updating image sizes.

We built a full-fletched mobile-friendly web applicationusing Meteor web framework~\cite{meteor}.
Meteor framework supports reactivity which makes the application update user interface based on actions
of other users in real time. This helps users see comments by other users as they happen, but can also see
progress during voting in real time.

@@

PeerMind source code is available under open source licence at \url{http://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{http://redacted.for.blind.review}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/peermind.png}
\caption{User interface of PeerMind web application. One can see three column structure, with commenting
section on the left, summary points in the middle, and proposed proposals with voting on the right.}
\label{fig:peer-mind}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/results.png}
\caption{Results of a vote in PeerMind web application. Results are shown as an average score through time of the vote.
A user can hover over the chart to see details at that time. Users can see these results in real time during voting.}
\label{fig:results}
\end{figure}

>>>>

We built a full-fletched mobile-friendly web application using Meteor web framework~\cite{meteor}.
Meteor framework supports reactivity which makes the application update user interface based on actions
of other users in real time. This helps users see comments by other users as they happen, but can also see
progress during voting in real time.

@@

PeerMind source code is available under open source licence at \url{https://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{https://redacted.for.blind.review}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/peermind.png}
\caption{User interface of PeerMind web application. One can see three column structure, with commenting
section on the left, summary points in the middle, and proposed proposals with voting on the right.}
\label{fig:peer-mind}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{figures/results.png}
\caption{Results of a vote in PeerMind web application. Results are shown as an average score through time of the vote.
A user can hover over the chart to see details at that time. Users can see these results in real time during voting.}
\label{fig:results}
\end{figure}
